\subsubsection{Aug 2022 Evaluation}
With the successfully processing of DP0.2 \citedsp{RTN-041}  PanDA was endorsed for DRP processing.
Some support issues need to be sorted out with BNL.

We may also have a developer alternative.

\subsubsection{July 2021 Evaluation}
A small group met on 15 July 2021 to asses the status of PanDA on the IDF and going forward.
We  concluded  that PanDA is functioning on IDF, though it certainly needs some more work.
We definitely will use this setup for DP0.2.
When DP0.2 is  successful we will endorse PanDA for sue  through DR1.
As a note DR1 is a general decision point for many technologies in line with our Rubin policy of keeping technology current operations.

On the specific points in \secref{sec:reqs}:
\begin{enumerate}
\item Documentation
\begin{itemize}
\item PanDA docs now appear on \url{https://panda-wms.readthedocs.io/en/latest/}
\item The User Guide in progress: \jira{DM-30805} see \url{https://panda-wms.readthedocs.io/en/latest/client/monitoring.html}
\item Panda for Rubin document in progress: \citeds{DMTN-168}
\item \href{https://docs.google.com/document/d/1J0Dxe_TJoIpWQm_izBY4Cz6mWkgLCVTZB6pZxkjS0Gg/edit}{ Sergey’s tutorial (in progress, to be turned into a dmtn) }
\end{itemize}
\item Workflow monitoring
\begin{itemize}
\item Currently at https://panda-doma.cern.ch/ site - it is difficult to understand.
\item Customization is possible but not demonstrated. Might want more campaign management inputs before customizing.
\item The design allows other tools to be built on top of it.
\item We need more training on using this monitoring site
\end{itemize}
\item Restart
\begin{itemize}
\item  There are automatic retries for transient issues.
\item Any changes to the workflow graph means a new graph needs to be made, submitted, and re-processed;  a BPS constraint for now PanDA doe snot really understand the DAG.
\begin{itemize}
\item Butler can recreate a graph removing the already run parts
\item PanDA can rerun the entire workflow - the jobs already done will start up and finish instantly (with start up time).
\end{itemize}

\end{itemize}
\item Logstash
\begin{itemize}
\item \emph{ Not done. }
\item The payload logs are now stored in a Google bucket. Work is needed to integrate with Google's log analysis tooling.

\end{itemize}
\item Troubleshooting failed jobs
\begin{itemize}
\item Triaging is done on the monitoring site.
\item Again we need more training on using the monitoring site for the execution team
\end{itemize}
\item  DOMA @ CERN  - IN2P3 bonus.
\begin{itemize}
\item IN2P3 setup was not attempted.  DOMA@CERN is used.
\item CERN test PanDA server was a bit overloaded by the traffic (many small jobs), but has been replaced by a beefier machine which should fix the problem.
\end{itemize}
\end{enumerate}

In addition to the above we note positively Jim Chiang has been successful in running Camera BPS jobs at SLAC via the same PanDA server as IDF
which was not in the original scope.


