\section{Goals and priorities for 2021}\label{sec:goals21}
A time line for these items should be agreed with BNL.

\subsection {High priority items } \label{sec:high}
\begin{enumerate}
\item Execution Butler integration. This is a blocker for DP0.2. (P0)
\item Documentations \& training (P1) : we need operator training,  what training do Atlas operators receive?
\item Allow panda workflow submission from data-int.lsst.cloud RSP environment (P1)
\item Setup Logstash or equivalent (P1) - decide on :
\begin{itemize}
\item Set up the ELK stack on Google
\item Or use Google-only Tooling. This might be the quickest but less portable.
\end{itemize}
\item BPS panda plug-in integration and refactoring (P1)
\begin{itemize}
\item Env var expansion, configuration file organization, etc may not be consistent with other BPS plugins.
\item Need to support BPS commands rather than custom scripts for bps report/cancel
\item Less hacks in general ..
\item BPS needs to expand its commands, e.g. retry, to allow panda integration
\item Needs time with Michelle Gower and Sergey working together to understand generic vs specific code.
\end{itemize}
\item BPS needs to support small job clustering, otherwise the panda server will be slow with small jobs (as we refused panda-specific workarounds). This can be a serious performance hit for DP0.2. (P1)
\begin{itemize}
\item This also needs work from DM side (Nate or Michelle)
\end{itemize}

\end{enumerate}

\subsection {Lower priority items (P2)}
Still needed and important but not as important as \secref{sec:high}:
\begin{enumerate}
\item Move the PanDA server from CERN to SLAC  (P2)
\begin{itemize}
\item This includes an Architecture review/tuning.  Google/Burwood may help if we deem that useful.
\end{itemize}
\item Attempt multi-site setup (P2)
\begin{itemize}
\item USDF, IDF, IN2P3, UKDF
\end{itemize}
\item Authentication. Currently at least two separate identities are needed for each user. (P2)
\begin{itemize}
\item Submission VM: this won't exist once we can submit from data-int
\item Panda-DOMA: integration work w/ Rubin auth is needed
\end{itemize}
\item We need a Support plan agreed with BNL(P2):
\item Currently we have only one Sergey who knows all things.  We are dead if Sergey goes on vacation.  Shuwei needs to become a full backup.
\item DMTN-168 needs an section on how IDF is setup (GKE etc) so we can better understand it.
\item On IDF, if  we expect more tuning, e.g. on kubernetes setup? Likely yes; do we continue to use  Burwood. This is ok at least for DP0.2 but its not free.
\end{enumerate}
